Visually pleasing knot projections

### 2022-06-08 inst/jma_rebuttal_review3.tex

\textcolor{blue}{I appreciate the sentiment, which I take to be a
  comment on the large amount of programming-oriented detail in the
  submission.  This reviewer evidently regards the knots in the
  submission as ``decent'', which I take to be a great compliment.  It
  is often difficult to know the correct balance between overly
  technical descriptions [which indeed often overlaps with the aims of
    a technical manual] and gushing conceptual big-picture thinking.
  However, I note that many of the comments below are essentially
  requests for clarifications of minor technical details of the
  implementation: and this would indicate that perhaps the balance
  should be shifted back toward the technical manual end of the
  spectrum.  The other observation I would make here is that the
  software package [27] is intended to be part of the submission (it
  is released under the GPL and is thus available for public use) and
  with this understanding, even a downbeat technical manual would have
  scholarly value in conjunction with the new software it describes.
  I want the editor and reviewer to know that in addressing the
  concerns below I have tried hard to answer not just ``what'' but
  also the ``why'' of the implementation.  \\ \\ Nevertheless, the cue
  above is a good one.  The two questions: (a) {\em what makes a knot
    plot attractive?}, and (b) {\em how best ... to achieve this?}
  are indeed profound, and were not addressed directly in the old
  manuscript.  In the revision I have prominently stated the questions
  in the introduction, and given a provocative, if brief, outline of
  my view.}

The problem starts with the basic curve representation:

Why use Bezier curves?

\textcolor{blue}{Most of the answer is in the manuscript: ``A Bezier
  curve is a visually pleasing polynomial path that can be used to
  specify the path of a knot projection; here cubic Bezier curves are
  used''.  However, Bezier curves are a natural choice for a number of
  reasons and I have added the following sentence: ``Bezier curves are
  a natural choice for working with mathematical knots for several
  reasons: they are familiar to many graphical workers; they have a
  natural and intuitive control system (usually called ``handles''),
  and are implemented in many graphical software suites''.  I do not
  wish to suggest that Bezier curves are the only parametrizations for
  working with knots; but they are a natural starting point, and
  AFAICS they have no serious disadvantages in this context, nor is
  there any obvious superior method.}

### 2022-06-08 inst/jma_rebuttal_review3.tex

Why use Bezier curves?

\textcolor{blue}{Most of the answer is in the manuscript: ``A Bezier
  curve is a visually pleasing polynomial path that can be used to
  specify the path of a knot projection; here cubic Bezier curves are
  used''.  However, Bezier curves are a natural choice for a number of
  reasons and I have added the following sentence: ``Bezier curves are
  a natural choice for working with mathematical knots for several
  reasons: they are familiar to many graphical workers; they have a
  natural and intuitive control system (usually called ``handles''),
  and are implemented in many graphical software suites''.  I do not
  wish to suggest that Bezier curves are the only parametrizations for
  working with knots; but they are a natural starting point, and
  AFAICS they have no serious disadvantages in this context, nor is
  there any obvious superior method.}

Why not use some other spline curve that guarantees G2-continuity?

\textcolor{blue}{I don't have a good answer to that, other than to
  point out that the focus of the manuscript was to investigate the
  visual appearance of knots using mathematical optimization routines.
  I do not wish to rule out using other G2-continuous splines, and it
  might be interesting some day to consider (e.g.) B-splines.  But as
  I say above, Bezier curves are a good starting point.}

### 2022-06-08 inst/jma_rebuttal_review3.tex

Some more detailed comments:

Page 3 line 42: ``...knots possess a line of symmetry (at least, the
diagrams do if the breaks are ignored), which ..."  -$>>$ ``...knots
possess a C2 rotation axis, which ..."

Page 4 lines 22-25: ``One plausible technique for creating knot
projections is to consider a two-dimensional projection of a knot's
embedding E in R3. However, this approach often results in poor visual
appearance: cusps or other displeasing effects can occur."  -$>>$ True!
- But what is the alternative, if the user has an entangled physical
knot in her hands?

\textcolor{blue}{Being able to render a nice optimized diagram
  corresponding to a physical knot that one has in one's hands is a
  reasonable wish.  But not one that I can fulfil.  Indeed, the
  package is predicated upon the notion that the diagram is the
  ``real'' object, and the (3D) knot itself is irrelevant.  Thus much
  of the package {\em prevents} the optimization routine from making
  Reidermeister moves [that is, changes that affect the topology of
    the diagram but not that of the 3D knot].  The operational reason
  for this is that the user specifies a particular diagram which the
  software then optimizes for appearance.  The manuscript includes two
  diagrams of $10_{125}$, the Perko pair, which show that sometimes
  one wants to preserve the topology of the diagram.}

### 2022-06-08 inst/jma_rebuttal_review3.tex

Page 4 line 45: Define ``nodes" !

\textcolor{blue}{``Nodes'' is a standard word in the context of Bezier
  curves. I have not used the word in any other sense in the
  manuscript and I think the text is clear as it stands.}

Page 4 line 48: ``However, if we can ensure that the radius of
curvature changes only by a small amount,..."  -$>>$ HOW can the user do
this?

\textcolor{blue}{It is not the user that stops large changes, it is
  the optimization routine and in particular the rather eclectic set
  of badness functions.  Incidentally, the ``keep nodes far from
  crossing points'' badness function is instrumental in stopping large
  changes of this type from occurring.\\ \\ OLD TEXT: However, if we
  can ensure that the radius of curvature changes only by a small
  amount, visual continuity---in the sense of absence of visible
  interruptions to a smoothly evolving strand---is
  preserved. \\ \\ NEW TEXT: However, because the optimization routine
  ensures that the radius of curvature changes only by a small
  amount, visual continuity---in the sense of absence of visible
  interruptions to a smoothly evolving strand---is
  preserved.\\ \\
}

### 2022-06-08 inst/jma_knot.tex
fixes #49
fixes #56

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{Inkscape}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection; here cubic Bezier curves are
used.  The software discussed here~\cite{hankin2020} allows one to
specify a knot in terms of its Bezier control points within inkscape,
import the object into R~\cite{rcore2021}, and then to use numerical
optimization techniques to improve the visual appearance of the knot.

@@

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  One consequence of this design choice is that
radius of curvature is not matched exactly across a node; the path is
not G2 smooth in CAD terminology.  However, if we can ensure that the
radius of curvature changes only by a small amount, visual
continuity---in the sense of absence of visible interruptions to a
smoothly evolving strand---is preserved.  At a crossing point it is
important that both the unbroken and broken strands (designated
``overstrand'' and ``understrand'' respectively) are smooth.  We would
like strand crossing points to be far from nodes, as this ensures
visual continuity of strands at crossing points, especially the
understrand (see Figure~\ref{two_trefoil_knots} for an example and
discussion).

>>>>

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{Inkscape}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection; here cubic Bezier curves are
used.  Bezier curves are a natural choice for working with
mathematical knots for several reasons: they are familiar to many
graphical workers; they have a natural and intuitive control system
(usually called ``handles''), and are implemented in many graphical
software suites.  The software discussed here~\cite{hankin2020} allows
one to specify a knot in terms of its Bezier control points within
inkscape, import the object into R~\cite{rcore2021}, and then to use
numerical optimization techniques to improve the visual appearance of
the knot.

@@

Here, knot paths are required to have Bezier handles that are
symmetrically placed with regard to nodes (this is a user-settable
option in inkscape).  One consequence of this design choice is that
radius of curvature is not matched exactly across a node; the path is
not G2 smooth in CAD terminology.  However, because the optimization
routine ensures that the radius of curvature changes only by a small
amount, visual continuity---in the sense of absence of visible
interruptions to a smoothly evolving strand---is preserved.  At a
crossing point it is important that both the unbroken and broken
strands (designated ``overstrand'' and ``understrand'' respectively)
are smooth.  We would like strand crossing points to be far from
nodes, as this ensures visual continuity of strands at crossing
points, especially the understrand (see Figure~\ref{two_trefoil_knots}
for an example and discussion).
